---
title: "p8105_hw6_jl6647"
author: "Jiatong Li"
date: "2023-11-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(boot)
library(modelr)
library(mgcv)
library(readxl)
```

Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

### bootstrap function
```{r}
set.seed(1)
boot_sample = function(weather_df) {
  sample_n(weather_df, size = nrow(weather_df), replace = TRUE)
}
```

### 5000 bootstrap samples
```{r}
boot_strap = weather_df |>  
  modelr::bootstrap(n = 5000) |> 
  mutate(
    mods = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    mods_beta = map(mods, broom::glance),
    mods_r2 = map(mods, broom::tidy)) |> 
  unnest(mods_r2, mods_beta) |> 
  dplyr::select(.id, term, estimate, r.squared) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin,
    beta_2 = prcp) 

res = boot_strap |> 
  summarise(r.squared = r.squared,
    log_beta12 = log(beta_1 * beta_2),
    log_beta01 = log(beta_0 * beta_1))
```

### CI for r-squared and log
```{r}
# calculate CI for r-squared and log
r2_ci = 
  quantile(pull(res,r.squared), probs = c(0.025,0.975)) |> 
  knitr::kable()

log_ci = 
  quantile(pull(res,log_beta01), probs = c(0.025,0.975)) |>  
  knitr::kable()
  
r2_ci
log_ci
```
### Distribution Plots
```{r}
r2_dist = res |> 
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(title = "Distribution of Bootstrapped R-squared Estimates", x = "R-squared", y = "Density")
r2_dist
```

This plot is a density plot of bootstrapped R-squared estimates. The distribution of the R-squared values is unimodal and shows a peak around 0.92, indicating that the majority of the bootstrapped samples have an R-squared value close to this number. Also, the distribution is slightly skewed to the left, but is approximately as normal distribution.

```{r}
b1b2_dist = res |> 
  ggplot(aes(x = log_beta12)) +
  geom_density() +
  labs(title = "Distribution of Bootstrapped log(beta1*beta2) Estimates", x = "log(beta1*beta2)", y = "Density")
b1b2_dist
```

This plot is a density plot of bootstrapped Log Beta Product estimates. The distribution appears to be left-skewed, which may be caused by the `NA` generated during the logarithm calculation.
```{r}
b0b1_dist = res |> 
  ggplot(aes(x = log_beta01)) +
  geom_density() +
  labs(title = "Distribution of Bootstrapped log(beta0*beta1) Estimates", x = "log(beta0*beta1)", y = "Density")
b0b1_dist
```

This plot is also a density plot of bootstrapped Log Beta Product estimates. It follows the normal distribution.

Problem 3
```{r}
birthweight = read_csv("birthweight.csv")
```
### Tidy the dataset
```{r}
birth = 
  birthweight |> 
  janitor::clean_names() |> 
  mutate(babysex = case_when(babysex == 1 ~ 'male',
                             babysex == 2 ~ 'female'),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         malform = case_when(malform == 0 ~ 'absent',
                             malform == 1 ~ 'present'),
         mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other")) |> 
  na.omit()
```
### Propose a regression model for birthweight

**First, I set all variables as predictors and do MLR**
```{r}
mlr = lm(bwt ~ ., data = birth)
mlr |> 
  broom::tidy() |> 
  knitr::kable()
```

**I make a plot of model residuals against fitted values**
```{r}
birth |> 
    add_predictions(mlr) |>  
    add_residuals(mlr) |> 
    ggplot(aes(x = pred, y = resid)) +
    geom_point()  + 
    geom_smooth(method = "lm") + 
    labs(title = "Residuals against fitted values", 
       x = "Fitted Values", 
       y = "Residuals")
```

From the plot it is clear to see that the slope is 0, so we need to select predictors in order to measure the relationship

**Compare your model to two others: One using length at birth and gestational age as predictors (main effects only), One using head circumference, length, sex, and all interactions (including the three-way interaction) between these**
```{r}
# model comparison 1
model_bg = lm(bwt ~ blength + gaweeks, data = birth) |> 
  broom::tidy() |> 
  knitr::kable()

# model comparison 2
model_bbb = lm(bwt ~ bhead * blength * babysex, data = birth) |> 
  broom::tidy() |> 
  knitr::kable()
```


